Effort and Delay Discounting in a Foraging Environment

### 2019-04-26 Cost2/Cost2_prereg_remake.Rmd
updated cog logs to match the rest (similar to cost 3 too)

dataAll <- data_frame(SubjID = files) %>%
  mutate(contents = map(SubjID, ~ read_csv(., col_types = cols())))  %>%
  mutate(Cost = substring(SubjID, 5, 8),
         Cost = case_when(Cost == "wait" ~ "Wait",
                          Cost == "cogT" ~ "Cognitive",
                          Cost == "phys" ~ "Physical",
                          Cost == "phea" ~ "Easy"),
         Cost = factor(Cost, levels = c("Physical", "Cognitive", "Wait", "Easy")),
         SubjID = substring(SubjID, 0, 3)) %>%
  unnest() %>%
  mutate(Half = ifelse(Block < 4, "Half_1", "Half_2"))

# # load cognitive effort group
# setwd('./data/Cost2_data/cog')
# temp = list.files(pattern="*.csv")
# cogDataLong = lapply(temp, read.csv, header = FALSE)
# 
# # load wait group
# setwd('../wait')
# temp = list.files(pattern="*.csv")
# waitDataLong = lapply(temp, read.csv, header = FALSE)
# 
# # load physical group
# setwd('../phys')
# temp = list.files(pattern="*.csv")
# physDataLong = lapply(temp, read.csv, header = FALSE)
# 
# # load pheasysical group
# setwd('../easy')
# temp = list.files(pattern="*.csv")
# easyDataLong = lapply(temp, read.csv, header = FALSE)

>>>>

dataAll <- tibble(SubjID = files) %>%
  mutate(contents = map(SubjID, ~ read_csv(., col_types = cols())))  %>%
  mutate(Cost = substring(SubjID, 5, 8),
         Cost = case_when(Cost == "wait" ~ "Wait",
                          Cost == "cogT" ~ "Cognitive",
                          Cost == "phys" ~ "Physical",
                          Cost == "phea" ~ "Easy"),
         Cost = factor(Cost, levels = c("Physical", "Cognitive", "Wait", "Easy")),
         SubjID = substring(SubjID, 0, 3)) %>%
  unnest() %>%
  mutate(Half = ifelse(Block < 4, "Half_1", "Half_2"))

subjList <- unique(dataAll$SubjID)
# # load cognitive effort group
# setwd('./data/Cost2_data/cog')
# temp = list.files(pattern="*.csv")
# cogDataLong = lapply(temp, read.csv, header = FALSE)
# 
# # load wait group
# setwd('../wait')
# temp = list.files(pattern="*.csv")
# waitDataLong = lapply(temp, read.csv, header = FALSE)
# 
# # load physical group
# setwd('../phys')
# temp = list.files(pattern="*.csv")
# physDataLong = lapply(temp, read.csv, header = FALSE)
# 
# # load pheasysical group
# setwd('../easy')
# temp = list.files(pattern="*.csv")
# easyDataLong = lapply(temp, read.csv, header = FALSE)
